Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-22 tex/paper1/paper1.tex
edits to the paper

\section{Analysis}\label{sec:anal}
We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figure \ref{fig:loc171193} shows the location of the regions on sample
images from the time range considered. {\bf These locations, selected
  by visual inspection, were chosen because they are representative of
  commonly observed structures in the corona.  Further,
  oscillatory power has been identified previously over sunspots and
  loop footpoints \citep{2002A&A...387L..13D} and moss structures
  \citep{2003ApJ...595L..63D}.  A quiet Sun region is also included
  for comparison.}
\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.  The spatial extent of
  the data is (-501'', -138'') in the x-direction, and (-80'', 107'')
  in the y-direction, in heliocentric cartesian co-ordinates.  The
  images show NOAA AR 1575 and some surrounding area.
  \citep{2006A&A...449..791T}.}
\label{fig:loc171193}
\end{figure}

@@

As has been shown above, the assumption of a Gaussian-distributed
(white) noise when a \PL\ \PS\ is actually present, coupled with too
low a confidence level, can lead to misleading results when looking
for oscillatory signals (Section \ref{ssec:corseis} and Figure
\ref{fig:comparison}).  The detection algorithms outlined in Section
\ref{sec:introduction} have yet to be tested assuming a background
\PL\ \PS, and so their efficacy is unknown.
\cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S} are
wavelet-based approaches, and the discussion Section
\ref{ssec:corseis} does suggest that a background \PL\ \PS\ will make
a significant difference to the number of wave detections found in the
data.

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  The {\it wave coherence} detection approach of
\cite{2008SoPh..252..321M} implement wave detection through finding
spatially contiguous regions of the corona which are coherent in a
given frequency range.  Oscillations that are detected propagating
along loops are often found by considering distance-time plots
\citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for
alternating brightening/darkening in those plots as a indicator of a
propagating wave.  This is essentially a coherence-based approach that
involves an implicit assessment of the likelihood that an oscillation
has been detected.  The basis of the assessment is a judgement that a
signal is seen in multiple contiguous pixels.  However, the results of
Section \ref{sec:anal} suggest that each pixel in these plots has a
background \PL\ \PS: the discussion of Section \ref{ssec:corseis}
therefore suggests that the significance of any claimed oscillation is
much reduced.  {\bf The wave coherence method of \cite{2008SoPh..252..321M}
uses a symmetric filter to estimate the coherence, in that oscillatory
power from either side of the central search frequency contributes the
same weight to the final result.  The effect of this filter in the
presence of a \PL\ \PS\ may be to bias detections to lower
frequencies.}

>>>>

\section{Analysis}\label{sec:anal}
We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figure \ref{fig:loc171193} shows the location of the regions on sample
images from the time range considered. {\bf These locations, selected
  by visual inspection, were chosen because they are representative of
  commonly observed structures in the corona.  Further,
  oscillatory power has been identified previously over sunspots and
  loop footpoints \citep{2002A&A...387L..13D} and moss structures
  \citep{2003ApJ...595L..63D}.  A quiet Sun region is also included
  for comparison.}
\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.  The spatial extent of
  the data is (-501'', -138'') in the x-direction, and (-80'', 107'')
  in the y-direction, in heliocentric cartesian co-ordinates.  The
  images show NOAA AR 11575 and some surrounding area.
  \citep{2006A&A...449..791T}.}
\label{fig:loc171193}
\end{figure}

@@

As has been shown above, the assumption of a Gaussian-distributed
(white) noise when a \PL\ \PS\ is actually present, coupled with too
low a confidence level, can lead to misleading results when looking
for oscillatory signals (Section \ref{ssec:corseis} and Figure
\ref{fig:comparison}).  The detection algorithms outlined in Section
\ref{sec:int} have yet to be tested assuming a background
\PL\ \PS, and so their efficacy is unknown.
\cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S} are
wavelet-based approaches, and the discussion Section
\ref{ssec:corseis} does suggest that a background \PL\ \PS\ will make
a significant difference to the number of wave detections found in the
data.

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  The {\it wave coherence} detection approach of
\cite{2008SoPh..252..321M} implement wave detection through finding
spatially contiguous regions of the corona which are coherent in a
given frequency range.  {\bf \cite{2008SoPh..252..321M} use a
  symmetric filter to estimate the coherence, in that oscillatory
  power from either side of the central search frequency contributes
  the same weight to the final result.  The effect of this filter in
  the presence of a \PL\ \PS\ may be to bias detections to lower
  frequencies.}  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for
alternating brightening/darkening in those plots as a indicator of a
propagating wave.  This is essentially a coherence-based approach that
involves an implicit assessment of the likelihood that an oscillation
has been detected.  The basis of the assessment is a judgement that a
signal is seen in multiple contiguous pixels.  However, the results of
Section \ref{sec:anal} suggest that each pixel in these plots has a
background \PL\ \PS: the discussion of Section \ref{ssec:corseis}
therefore suggests that the significance of any claimed oscillation is
much reduced.
